DATA 621---Business Analytics and Data Mining

### 2020-09-16 HW1/HW1_draft_kellogg.Rmd
fixed training set backward selection

```{r performance, echo=FALSE, message=FALSE, warning=FALSE}
# Model accuracy
results = data.frame(Models = c("Model #1: Backwards" , "Model #2: Pairwise", "Model #3: K-fold"),
                R.squared = c(mod_sum1[["r.squared"]], stmr2, mod_sum[["r.squared"]]), 
                adj.R.squared = c(mod_sum[["adj.r.squared"]], stmar2, mod_sum[["adj.r.squared"]]),
                AIC = c(AIC(lm_1), AIC(stepModel), AIC(step.model$finalModel)),
                RSME = c(sqrt(mean((train_set$TARGET_WINS - pred_lm1)^2)), stmRMSE,
                         sqrt(mean((stepdata$TARGET_WINS - pred_step.model)^2))))
results %>% knitr::kable(digits = 3L, caption = 'Performance Statistics & Error Measure of Models' )
```

>>>>

```{r performance, echo=FALSE, message=FALSE, warning=FALSE}
# Model accuracy
results = data.frame(Models = c("Model #1: Backwards" , "Model #2: Pairwise", "Model #3: K-fold"),
                R.squared = c(mod_sum1[["r.squared"]], stmr2, mod_sum[["r.squared"]]), 
                adj.R.squared = c(mod_sum[["adj.r.squared"]], stmar2, mod_sum[["adj.r.squared"]]),
                AIC = c(AIC(lm_1), AIC(stepModel), AIC(step.model$finalModel)),
                RSME = c(sqrt(mean((train_df2$TARGET_WINS - pred_lm1)^2)), stmRMSE,
                         sqrt(mean((stepdata$TARGET_WINS - pred_step.model)^2))))
results %>% knitr::kable(digits = 3L, caption = 'Performance Statistics & Error Measure of Models' )
```
